---
title: "Pizza"
author: "Caeden Kullander"
date: "2025-03-16"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Introduction

pizza_barstool is a dataset about pizza places and their reviews. I found it on TidyTuesday. It pulls data from the “One Bite” app. This data includes review information from critics and the public, as well as location and price rating information.
I want to explore the relationships between location, price ratings, community reviews, critic reviews, and number of reviews and how these are correlated with each other. 
Specifically, I want to know how much community reviews differ from critic reviews, and how location and price impact these correlations.

## 2. Data

```{r echo=FALSE, message=FALSE}
pizza <- read.csv(file = "data/pizza_barstool.csv")
```


```{r echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidymodels)
glimpse(pizza)
```

## 3. Data analysis plan

To answer my questions, I plan to use the variables for average scores for critics and community. I plan to compare visualisations between the two, and also filter/mutate for specific geographical areas to see how ratings compare in various locations.

Does the number of reviews correlate with the average review score?

```{r echo=FALSE}
library(ggplot2)
ggplot(data=pizza, mapping=aes(x = review_stats_community_average_score, y = review_stats_community_count)) +
  geom_point() +
  labs(x="Average Community Rating", y="Total Community Reviews")
```

There is certainly some correlation there, but this display shows that many of the restaurants have very few reviews.


How does price level correlate with community ratings and critic ratings? How are the correlations different?
```{r echo=FALSE}

ggplot(data=pizza, mapping=aes(y = review_stats_community_average_score, x = price_level, alpha = 0.2)) +
  geom_point() +
  labs(y="Average Community Rating", x="Price rating")
```

```{r echo=FALSE}

ggplot(data=pizza, mapping=aes(y = review_stats_critic_average_score, x = price_level)) +
  geom_point() +
  labs(y="Average Critic Rating", x="Price rating")
```

The two are surprisingly similar, with very little notable difference.



```{r zero_filter}
pizza <- pizza %>%
  mutate("review_stats_community_count" = case_when(review_stats_community_count != 0 ~ review_stats_community_count)) %>%
  drop_na()

pizza %>%
  count(review_stats_community_count)
```



**Now I want to analyze the difference in ratings depending on whether a restaurant is in New York or not.**

```{r nyc}
pizza <- pizza %>%
  mutate("nyc" = ifelse(city=="New York" | city=="New York City", "yes", "no"))
```

```{r message=FALSE}
ggplot(data=pizza, mapping=aes(x = review_stats_all_average_score, fill = nyc)) +
  geom_histogram() +
  facet_wrap(nyc~.) +
  labs(y="Average Community Rating", x="Price rating")
```

**The two are still quite similar aside from NYC having larger spikes and more observations in total.**



Now I want to see how number of reviews is correlated with review score. I expect that with more reviews, there will be a higher average, as people often tend to cluster towards high quality restaurants, but I may be surprised.

```{r warning=FALSE}
ggplot(data=pizza, mapping=aes(y = review_stats_community_average_score, x = review_stats_community_count, alpha=0.5)) +
  geom_jitter() +
  xlim(0, 250) +
  geom_smooth()
  labs(y="Community Average Rating", x="Community Review Count")
```

**While there is a large cluster of high ratings where there are few reviews, whenever there is a high number of reviews the ratings are also high. I'm curious about this correltaion, so let's make a model for it.**


```{r}
linear_reg() %>%
  set_engine("glm") %>%
  fit(review_stats_community_average_score ~ review_stats_community_count, data = pizza) %>%
  tidy()
```
**Starting at 6.89 for every review, the community average rating is expected to be 0.01 higher.**



I want to now do the same visualisation and model, but this time filter out the observations with only a very small number of reviews. First, I'll filter out anything with less than five reviews and see where that gets me. 


```{r filtered_pizza}
filtered_pizza <- pizza %>%
  filter(review_stats_community_count >= 5)

```


```{r warning=FALSE}
ggplot(data=filtered_pizza, mapping=aes(y = review_stats_community_average_score, x = review_stats_community_count, alpha=0.5)) +
  geom_jitter() +
  xlim(0, 250) +
  geom_smooth()
  labs(y="Community Average Rating", x="Community Review Count")
```

```{r}
linear_reg() %>%
  set_engine("glm") %>%
  fit(review_stats_community_average_score ~ review_stats_community_count, data = filtered_pizza) %>%
  tidy()
```

This is interesting. It raised the intercept but reduced the slope. Looking at the data, it seems that it plateaus after around 50 reviews. Let's try filtering for only data with 5-50 reviews.

```{r}
few_pizza <- filtered_pizza %>%
  filter(review_stats_community_count <= 50)
```


```{r warning=FALSE}
ggplot(data=few_pizza, mapping=aes(y = review_stats_community_average_score, x = review_stats_community_count, alpha=0.5)) +
  geom_jitter() +
  geom_smooth()
  labs(y="Community Average Rating", x="Community Review Count")
```



```{r}
linear_reg() %>%
  set_engine("glm") %>%
  fit(review_stats_community_average_score ~ review_stats_community_count, data = few_pizza) %>%
  tidy()
```

This lowered the intercept but raised the slope. It might be slightly more helpful, but through all of this I'm seeing that it makes sense to simply eat at the restaurants with a high number of reviews, as they all tend to have good ratings. While a restaurant with a moderate number of reviews have a chance of being good, the restaurants with massive numbers are consistently rated highly. Basically, go straight to where it plateaus, becuase there is no reason not to. Then again, maybe there could be some reason not to. Perhaps these restaurants are more expensive. Let's check.


```{r}
many_pizza <- pizza %>%
  filter(review_stats_community_count >= 50)
```


```{r echo=FALSE}

ggplot(data=many_pizza, mapping=aes(y = review_stats_community_average_score, x = price_level, alpha = 0.2)) +
  geom_point() +
  labs(y="Average Community Rating", x="Price Level")
```

Nope, none of these go above 2. This means that we want a restaurant with a price level of 2, and a large number of reviews. 


