---
title: "Project"
author: "Caeden Kullander"
date: "2025-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

pizza_barstool is a dataset about pizza places and their reviews. I found it on TidyTuesday. It pulls data from the “One Bite” app. This data includes review information from critics and the public, as well as location and price rating information.
I want to explore the relationships between location, price ratings, community reviews, critic reviews, and number of reviews and how these are correlated with each other. 




```{r}
pizza <- read.csv(file = "data/pizza_barstool.csv")
```


```{r}
glimpse(pizza)
```

Question: Does the number of reviews corelate with the average review score?

```{r}
library(ggplot2)
ggplot(data=pizza, mapping=aes(x = review_stats_community_average_score, y = review_stats_community_count)) +
  geom_point() +
  labs(x="Average Community Rating", y="Total Community Reviews")
```

There is certainly some correlation there, but this display shows that many of the restauants have very few reviews.













