---
title: "Project"
author: "Caeden Kullander"
date: "2025-03-16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Introduction

pizza_barstool is a dataset about pizza places and their reviews. I found it on TidyTuesday. It pulls data from the “One Bite” app. This data includes review information from critics and the public, as well as location and price rating information.
I want to explore the relationships between location, price ratings, community reviews, critic reviews, and number of reviews and how these are correlated with each other. 
Specifically, I want to know how much community reviews differ from critic reviews, and how location and price impact these correlations.

## 2. Data

```{r echo=FALSE}
pizza <- read.csv(file = "data/pizza_barstool.csv")
```


```{r echo=FALSE}
library(dplyr)
glimpse(pizza)
```

## 3. Data analysis plan

To answer my questions, I plan to use the variables for average scores for critics and community. I plan to compare visualisations between the two, and also filter/mutate for specific geographical areas to see how ratings compare in various locations.

Does the number of reviews correlate with the average review score?

```{r echo=FALSE}
library(ggplot2)
ggplot(data=pizza, mapping=aes(x = review_stats_community_average_score, y = review_stats_community_count)) +
  geom_point() +
  labs(x="Average Community Rating", y="Total Community Reviews")
```

There is certainly some correlation there, but this display shows that many of the restaurants have very few reviews.


How does price level correlate with community ratings and critic ratings? How are the correlations different?
```{r echo=FALSE}

ggplot(data=pizza, mapping=aes(y = review_stats_community_average_score, x = price_level)) +
  geom_point() +
  labs(y="Average Community Rating", x="Price rating")
```

```{r echo=FALSE}

ggplot(data=pizza, mapping=aes(y = review_stats_critic_average_score, x = price_level)) +
  geom_point() +
  labs(y="Average Critic Rating", x="Price rating")
```

The two are surprisingly similar, with very little notable difference.





