---
title: "Project proposal"
author: "Caeden Kullander"
output: github_document
---

```{r load-packages, message = FALSE, echo=FALSE}
library(tidyverse)
library(broom)
```


***Dear Professor Sullivan, I could not get the read.csv to work in this file. However, it worked fine in a different file that I was testing in. It is an Rmd file named "Project". Couldn't see any difference between the two, and I wanted to include something that was functional.***


## 1. Introduction
pizza_barstool is a dataset about pizza places and their reviews. I found it on TidyTuesday. It pulls data from the “One Bite” app. This data includes review information from critics and the public, as well as location and price rating information.
I want to explore the relationships between location, price ratings, community reviews, critic reviews, and number of reviews and how these are correlated with each other. 
Specifically, I want to know how much community reviews differ from critic reviews, and how location and price impact these correlations.





## 2. Data

```{r echo=FALSE}
pizza <- read.csv(file = "data/pizza_barstool.csv")
```

```{r echo=FALSE}
library(dplyr)
glimpse(pizza)
```



## 3. Data analysis plan








