---
title: "Pizza"
author: "Caeden Kullander"
institute: "Houghton University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(ggplot2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/Pizza.JPEG", title_slide_text_color = "black"
)
```

```{r load-data, include=FALSE}
pizza <- read_csv(file = "pizza_barstool.csv")
```

```{r nyc, include=FALSE}
pizza <- pizza %>%
  mutate("nyc" = ifelse(city=="New York" | city=="New York City", "nyc", "not nyc"))
```

#Pizza
- The goal is to figure out what impacts pizza ratings so we can find the best restaurants.

- Motivation? College students everywhere need pizza, and they need to know how to find the best pizza.

- I found this data from Tidy Tuesday. It pulls from the "One Bite" pizza ratings app.

---
#Let's try Geographical!
--

.right-column[


NYC sucks!
```{r echo=FALSE, message=FALSE}
ggplot(data=pizza, mapping=aes(x = review_stats_all_average_score, fill = nyc)) +
  guides(fill="none") +
  geom_histogram() +
  facet_wrap(nyc~.) +
  labs(title = "New York City Pizza Ratings", x="Average Community Rating", legend = FALSE)
```
]
.left-column[
```{r echo=FALSE}
pizza %>%
  group_by(nyc) %>%
  summarise(med_rating =median(review_stats_community_average_score), mean_rating =mean(review_stats_community_average_score))
```


**New York does slightly worse on average.**
]
---
#Price level with Community Rating
```{r echo=FALSE}
ggplot(data=pizza, mapping=aes(y = review_stats_community_average_score, x = price_level, alpha = 0.2)) +
  geom_point(color="blue") +
  labs(y="Average Community Rating", x="Price level")

```
---
#Price rating with Critic Rating
```{r echo=FALSE}
ggplot(data=pizza, mapping=aes(y = review_stats_critic_average_score, x = price_level)) +
  geom_point(color="red") +
  labs(y="Average Critic Rating", x="Price level")
```

---
#There aren't many Critic Ratings

let's take a look at what the issue may be.

--
```{r echo=FALSE}
pizza %>%
  count(review_stats_critic_count)
```
**Oh dear! We don't have enough critic ratings.**

---
#Do we have the same issue with community ratings?
--
```{r echo=FALSE}
pizza %>%
  count(review_stats_community_count)
```
Looks like we'll be okay. However, we will go ahead and remove all of observations without any community reviews.
```{r echo=FALSE}
pizza <- pizza %>%
  mutate("review_stats_community_count" = case_when(review_stats_community_count != 0 ~ review_stats_community_count)) %>%
  drop_na()
```

---
##How does the total number of reviews affect the average review rating?

--
```{r echo=FALSE, fig.height=3, fig.width=4.4, message=FALSE, warning=FALSE}
ggplot(data=pizza, mapping=aes(y = review_stats_community_average_score, x = review_stats_community_count, alpha=0.5)) +
  geom_jitter() +
  xlim(0, 250) +
  geom_smooth() +
  labs(title="Community Reviews", y="Average Rating", x="Review Count")
```


---
#Let's make a model
```{r echo=FALSE}
linear_reg() %>%
  set_engine("glm") %>%
  fit(review_stats_community_average_score ~ review_stats_community_count, data = pizza) %>%
  tidy()
```

- Average review score = 6.89 + 0.01*total reviews

- Starting at 6.89, we would expect the rating to go up by 0.01 for each additional review.

---
#Keep this in mind
##Model for between 5 and 50 reviews

```{r filtered_pizza, include=FALSE, echo = FALSE}
fifty_pizza <- pizza %>%
  filter(review_stats_community_count >= 5 & review_stats_community_count <= 50)
```

```{r echo=FALSE}
linear_reg() %>%
  set_engine("glm") %>%
  fit(review_stats_community_average_score ~ review_stats_community_count, data = fifty_pizza) %>%
  tidy()
```

- Average review score = 6.73 + 0.03*total reviews

- Starting at 6.73, we would expect the rating to go up by 0.03 for each additional review.

---
#Conclusion


- New York isn't necessarily better.

- Mid-range prices are ideal (especially for college students).

- More reviews is generally good.
--

- Critics are essentially useless.
